[Re] Adaptive properties of differential learning rates for positive and negative outcomes

### 2018-06-13 Bavard-Thero-2018.tex
Add files via upload
We added one sentence on the results section according to one of the reviewers' advice.

    \usepackage{authblk}
                        \author[1]{Sophie Bavard}
                    \author[1]{Héloïse Théro}
                            \affil[1]{Laboratoire de Neurosciences Cognitives et Computationnelles (ENS -
INSERM), Département d'Études Cognitives, École normale supérieure, PSL
Research University, 29 rue d'Ulm, 75005 Paris, France}

@@

The only discrepancy we found was in Figure \ref{fig:figure4}A.
Although the general pattern was replicated, our learning curves
appeared smoother than in the reference article. As the number of
simulations were not explicitly specified for this figure, we cannot
know if this is due to us running a higher number of simulations than
the reference article, or from another difference in model
implementation.

>>>>

    \usepackage{authblk}
                        \author[1]{Sophie Bavard}
                    \author[1]{Héloïse Théro}
                            \affil[1]{Laboratoire de Neurosciences Cognitives Computationnelles (ENS -
INSERM), Département d'Études Cognitives, École normale supérieure, PSL
Research University, 29 rue d'Ulm, 75005 Paris, France}

@@

The only discrepancy we found was in Figure \ref{fig:figure4}A.
Although the general pattern was replicated, our learning curves
appeared smoother than in the reference article. As the number of
simulations were not explicitly specified for this figure, we cannot
know if this is due to us running a higher number of simulations than
the reference article, or from another difference in model
implementation. However, we obtained similar noise when dividing 
the number of simulations by ten, suggesting the original authors 
used around 500 iterations for this part of the figure.
